%-------------------------
% "Resume in Latex"
% Template Author: Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{textcomp}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%















\begin{document}

\begin{center}
    \textbf{\Huge \scshape Donnell Fulwiler} \\ \vspace{1pt}
    \small 512-966-5734 $|$ \href{mailto:dbfulwiler@gmail.com}{\underline{dbfulwiler@gmail.com}} $|$ 
    \href{https://linkedin.com/in/donnell-fulwiler}{\underline{linkedin.com/in/donnell-fulwiler}} $|$
    \href{https://github.com/donnell-f}{\underline{github.com/donnell-f}} $|$
    \href{https://people.tamu.edu/~donnellfulwiler}{\underline{people.tamu.edu/\texttildelow{}donnellfulwiler}} $|$
    Austin, TX
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {St. Dominic Savio CHS}{Austin, TX}
      {High School Diploma, $98.41$ GPA}{Aug. 2019 -- May 2023}
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {B.S. Computer Science, Statistics Minor, $3.93$ GPA, Class of 2027}{Aug. 2023 -- May 2027}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Science Intern (Remote)}{Summer 2025}
      {Kaizen Action LLC.}{Palo Alto, CA}
      \resumeItemListStart
        \resumeItem{Developed several tactical analysis algorithms and ran them on various securities. Many algorithms achieved +10\% ROI.}
        \resumeItem{Used Pandas and Numpy extensively to analyze gigabytes of data.}
        \resumeItem{Used Tensorflow to create and train a hidden markov model for time series analysis.}
        \resumeItem{Used various econometric models such as GARCH, EGARCH, ARMA, and ARIMA to model volatility clustering and trends in certain securities. Certain models achieved 85\% accuracy in certain binary classification tasks.}
    \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Research Assistant}{Aug. 2025 -- Present}
      {Texas A\&M University}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Currently using CNNs and other image recognition algorithms to rapidly identify patterns and diagnostic information in bacteria.}
        \resumeItem{Working with a team of 8 as one of two machine learning experts.}
        \resumeItem{I utilize Python, Tensorflow, and Pandas on a daily basis.}
      \resumeItemListEnd

    \resumeSubheading
      {CSCE 120 TA}{Aug. 2025 -- Present}
      {Texas A\&M University}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Leading a lab of approximately 30 students. I give small lectures, create slides, etc. every week.}
        \resumeItem{I have helped hundreds of students debug and diagnose their C++ code.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gjallarhorn} $|$ \emph{C\#, MS Forms}}{July 2017}
          \resumeItemListStart
            \resumeItem{Developed a Runic transcription algorithm that can translate between 3 different types of Runic alphabets.}
            \resumeItem{Can transliterate any runic inscription written between 300 AD -- 1000 AD.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Neural Network from Scratch} $|$ \emph{Numpy, Python, tensor calculus}}{Feb. 2021 -- Jan 2022}
          \resumeItemListStart
            \resumeItem{Made a neural network from scratch using only self-taught tensor calculus knowledge and the NumPy Python library.}
            \resumeItem{The neural network had three layers, could recognize sinusoidal patterns in data. Trained using simple gradient descent.}
            \resumeItem{The neural network achieved 98\% accuracy in its task.}
            \resumeItem{Wrote a research paper on the project. Got featured in school newsletter and almost published.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Interactive x86 Tutorial} $|$ \emph{Git, Github, React, x86 Assembly, MySQL}}{Sep. 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Me and my friend Niel are currently working on an interactive, online, gamified x86 tutorial.}
            \resumeItem{Frontend is React based. Version control using Git. User data will be stored in a MySQL database.}
            \resumeItem{The goal is to make learning x86 assembly engaging, fun, and easy.}
            \resumeItem{Currently teaching x86 assembly in Intel syntax only.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, JavaScript, HTML/CSS, R, C\#, Haskell, Bash} \\
     \textbf{Frameworks}{: React, Node.js, Vite} \\
     \textbf{Developer Tools}{: Git, VS Code, Visual Studio, IntelliJ, Vim, Neovim, Linux} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Tensorflow, Keras, Pandas, Sqlite, Selenium, Playwright}\\
     \textbf{Skills}{: Machine Learning, AI, NLP, Regression, Classification, Web Scraping, Data Science}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
