%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (template)
% Edited for : Donnell Fulwiler
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
% \usepackage[empty]{fullpage}
\usepackage[margin=0.15in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\large \scshape Donnell Fulwiler} \\ \vspace{1pt}
    \small
    512-966-5734 $|$
    \href{mailto:dbfulwiler@gmail.com}{\underline{dbfulwiler@gmail.com}} $|$
    \href{https://donnell.info/}{\underline{https://donnell.info}} $|$
    \href{https://www.linkedin.com/in/donnell-fulwiler/}{\underline{linkedin.com/in/donnell-fulwiler}} $|$
    \href{https://github.com/donnell-f}{\underline{github.com/donnell-f}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {B.S. Computer Science; Minor in Statistics; GPA: 3.93 / 4.00}{Aug. 2023 -- May 2027}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Research Assistant}{2025 -- Present}
      {Chemical Engineering, Texas A\&M University}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Designing convolutional neural network pipelines in Python (TensorFlow, PyTorch) to recognize subtle morphological patterns in bacterial microscopy images.}
        \resumeItem{Collaborating with graduate researchers to build reproducible ML workflows, manage large labeled image datasets, and track model performance while adhering to NDA constraints.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Teaching Assistant, CSCE 120}{2025 -- Present}
      {Texas A\&M University}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Lead weekly C++ programming labs for a section of \textasciitilde40 students and support hundreds of students across the course through office hours and online help.}
        \resumeItem{Reinforce core CS concepts---control flow, functions, pointers, and basic data structures---through live coding, debugging sessions, and one-on-one mentoring.}
        \resumeItem{Built and maintained \emph{Gradescope Sleuth}, an internal plagiarism-detection tool that enabled the teaching team to uncover roughly 10x more academic integrity violations per assignment with less manual effort.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Science Intern}{Summer 2025}
      {Kaizen Action LLC}{Remote}
      \resumeItemListStart
        \resumeItem{Engineered and backtested tactical trading algorithms on equities and other securities, with several strategies achieving over 15\% simulated ROI on historical data.}
        \resumeItem{Processed multi-gigabyte financial time series using Python, pandas, and NumPy to clean, aggregate, and generate engineered features at scale.}
        \resumeItem{Applied econometric models (ARMA/ARIMA, GARCH, EGARCH) to capture volatility clustering and directional trends, reaching up to 85\% accuracy on selected binary classification tasks.}
        \resumeItem{Experimented with TensorFlow-based Hidden Markov Models to model regime shifts and improve the robustness of trading signals.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Gradescope Sleuth} $|$ \emph{Python, Selenium, SQLite, Regex, LRU Cache}}{2025}
      \resumeItemListStart
        \resumeItem{Automates retrieval of programming assignments from Gradescope using Selenium and consolidates submissions into a local SQLite database for analysis.}
        \resumeItem{Implements a custom pattern-matching engine with optimized regular expressions and an LRU cache to efficiently surface suspiciously similar code segments.}
        \resumeItem{Enabled the CSCE 120 teaching team to identify roughly 10x more plagiarism cases per assignment while significantly reducing manual review time.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Personal Web Server} $|$ \emph{React, Node.js, Express.js, Caddy, AWS Lightsail, Appwrite}}{2025}
      \resumeItemListStart
        \resumeItem{Host two production web applications on an Amazon Lightsail VPS using Caddy as a reverse proxy with automatic TLS via Let's Encrypt.}
        \resumeItem{Developed \href{https://donnell.info/}{\underline{donnell.info}} as a static React portfolio site showcasing projects, coursework, and writing.}
        \resumeItem{Built a secure React-based homework instruction portal for CSCE 120, using Google OAuth via Appwrite and an Express.js backend to gate access to course materials.}
        \resumeItem{Implemented ``AI traps'' in assignment text that only appear when copied to the clipboard, helping instructors detect LLM-generated work at scale.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{ExSELLence POS} $|$ \emph{React, Node.js, Express.js, PostgreSQL, Google OAuth, Google Translate, OpenWeather}}{2025}
      \resumeItemListStart
        \resumeItem{Collaborated with a team of five to design and build a point-of-sale web application targeting small retailers.}
        \resumeItem{Implemented a responsive React frontend and RESTful Express.js API backed by PostgreSQL to manage transactions, inventory, and customer data.}
        \resumeItem{Integrated Google OAuth for authentication and used Google Translate and OpenWeather APIs to localize the interface and enhance the checkout experience for diverse users.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Python, Java, Haskell, JavaScript, SQL, HTML, CSS} \\
     \textbf{Frameworks \& Libraries}{: React, Node.js, Express.js, TensorFlow, NumPy, pandas, Selenium} \\
     \textbf{Databases}{: PostgreSQL, SQLite3} \\
     \textbf{Tools \& Platforms}{: Git, Linux, Amazon Lightsail, Caddy, Appwrite} \\
     \textbf{Domains}{: Machine Learning, Time Series Analysis, Econometrics}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
